Guide to repository of supplementary resources

### 2022-06-09 index.Rmd
fixing stuff

---
title: "Index"
author: "Owen Petchey"
date: "6/9/2022"
output: html_document
---

[supplement](./experiments/2_supplement/supplement.html)

>>>>

---
title: "Guide to repository of supplementary resources"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

This is a guide to a repository containing various resources associated with the publication **Functional diversity can facilitate the collapse of an undesirable ecosystem state**.

[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)

[The Supplementary Report (HTML page)](./experiments/2_supplement/supplement.html)

[HTML page about how to reproduce the research.](./docs/How_to_reproduce.html)

[Some animations of results (HTML page)](./experiments/3_animate/report.html)
